The Dynamics of Normalization Reweighting (target journal: Neuron)

### 2022-06-14 manuscript.Rmd
Analysis updates

---
title: 'The Dynamics of Normalization Reweighting (target journal: Neuron)'
author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning,
  Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes 
    toc: false   
    keep_tex: true
  word_document: default
  html_document: default
---

@@

runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
processraw <- 1  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours

plotsmoothed <- 0 # either plot the raw data (0), or a smoothed spline (1)

@@

if (processraw==1){

@@

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
    if (s < 10){untar(paste(datadir, 'S0', s, '.tar', sep = ''), exdir = tempdir)}
    if (s > 9){untar(paste(datadir, 'S', s, '.tar', sep = ''), exdir = tempdir)}

@@

    for (block in 1:length(d)) {
      EEGdata <- read.csv(paste(tempdir, d[block], sep = ''), header = TRUE)

@@

      # epoch the data, Fourier transform and store
      triggertimes <- (1:40) * 0
      counter <- 0
      for (n in 1000:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
      for (n in 1:nrow(EEGdata)) {
        if (EEGdata$Trigger[n] %in% legaltriggers) {
          counter <- counter + 1
          triggertimes[counter] <- n
        }
      }

      for (tr in 1:counter) {
        cond <- EEGdata$Trigger[triggertimes[tr]] / 10
        condcounter[cond] <- condcounter[cond] + 1
        for (ch in 1:64){
        temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-1499, ch + 2])
        temp <- temp - mean(temp[501:1500])   # baseline subtraction to remove DC component
        allsamples[condcounter[cond],cond,ch,1:(1000*duration)] <- as.vector(rowMeans(temp))
        }
      }
    }
allsamples[which(is.na(allsamples))] <- 0     # remove any NaN values
meanwaveforms <- array(0,dim=c(14,64,14000))
    for (cond in 1:14){
      for (ch in 1:64){
        temp <- allsamples[1:condcounter[cond],cond,ch,]
        allspec <- matrix(0,nrow=condcounter[cond],ncol=10000)
        for (trial in 1:condcounter[cond]){
          allspec[trial,] <- fft(temp[trial,2501:12500])/10000
        }
        targetresps <- allspec[,tindex]
        maskresps <- allspec[,mindex]
      if (sum(abs(targetresps))>0){  
      tempxy <- data.frame(Re(targetresps),Im(targetresps))
      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      i1 <- (D<3)
      tempxy <- data.frame(Re(maskresps),Im(maskresps))
      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      i2 <- (D<3)
      i <- which((i1*i2)>0)
        meanwaveforms[cond,ch,] <- colMeans(temp[i,])
      }
      }
    }

     save(file = paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))

    for (block in 1:length(d)){file.remove(paste0(tempdir, d[block]))}

  }
}
}
}
}

if (runcode==1){
#   d <- dir('temp/VilidaiteProcessed/')
#   allwaves <- array(0,dim=c(length(d),14,64,14000))
#     load(paste0('temp/VilidaiteProcessed/',d[s]))
#     allwaves[s,,,] <- meanwaveforms
#   meanwaveforms <- array(0,dim=c(14,64,14000))
#   alltarget <- matrix(0,nrow=14,ncol=64)
#   allmask <- matrix(0,nrow=14,ncol=64)
#     for (cond in 1:14){
#       for (ch in 1:64){
#         temp <- allwaves[,cond,ch,]
#         allspec <- matrix(0,nrow=length(d),ncol=10000)
#         for (subj in 1:length(d)){
#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
#         targetresps <- allspec[,tindex]
#         maskresps <- allspec[,mindex]
#       if (sum(abs(targetresps))>0){  
#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
#       i1 <- (D<3)
#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
#       i2 <- (D<3)
#       i <- which((i1*i2)>0)
#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
#         alltarget[cond,ch] <- spec[tindex]
#         allmask[cond,ch] <- spec[mindex]
# targetchannels <- match(targetelectrodes, electrodes) - 2
# elecave <- colMeans(meanwaveforms[6,targetchannels,])
# binwidth <- 1000
# f1 <- 7
# tindex <- 1 + f1*(binwidth/1000)
# fspec <- elecave*0
# for (t in 1:(length(elecave)-binwidth)){
#   temp <- elecave[t:(t+binwidth-1)]
#   spec <- fft(temp)/binwidth
#   fspec[t] <- abs(spec[tindex])
# elecave <- colMeans(meanwaveforms[13,targetchannels,])
# binwidth <- 1000
# f1 <- 7
# tindex <- 1 + f1*(binwidth/1000)
# fspec2 <- elecave*0
# for (t in 1:(length(elecave)-binwidth)){
#   temp <- elecave[t:(t+binwidth-1)]
#   spec <- fft(temp)/binwidth
#   fspec2[t] <- abs(spec[tindex])
# times <- -499:13500
# plot(times,fspec,type='l',col=colpal[1])
# lines(times,fspec2,col='green')
#   d <- dir('temp/VilidaiteProcessed/')
#   allwaves <- array(0,dim=c(length(d),14,64,14000))
#     load(paste0('temp/VilidaiteProcessed/',d[s]))
#     allwaves[s,,,] <- meanwaveforms
#   meanwaveforms <- array(0,dim=c(14,64,14000))
#   alltarget <- matrix(0,nrow=14,ncol=64)
#   allmask <- matrix(0,nrow=14,ncol=64)
#     for (cond in 1:14){
#       for (ch in 1:64){
#         temp <- allwaves[,cond,ch,]
#         allspec <- matrix(0,nrow=length(d),ncol=10000)
#         for (subj in 1:length(d)){
#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
#         targetresps <- allspec[,tindex]
#         maskresps <- allspec[,mindex]
#       if (sum(abs(targetresps))>0){  
#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
#       i1 <- (D<3)
#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
#       i2 <- (D<3)
#       i <- which((i1*i2)>0)
#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
#         alltarget[cond,ch] <- spec[tindex]
#         allmask[cond,ch] <- spec[mindex]
# targetchannels <- match(targetelectrodes, electrodes) - 2
# elecave <- colMeans(meanwaveforms[6,targetchannels,])
# binwidth <- 1000
# f1 <- 7
# tindex <- 1 + f1*(binwidth/1000)
# fspec <- elecave*0
# for (t in 1:(length(elecave)-binwidth)){
#   temp <- elecave[t:(t+binwidth-1)]
#   spec <- fft(temp)/binwidth
#   fspec[t] <- abs(spec[tindex])
# elecave <- colMeans(meanwaveforms[13,targetchannels,])
# binwidth <- 1000
# f1 <- 7
# tindex <- 1 + f1*(binwidth/1000)
# fspec2 <- elecave*0
# for (t in 1:(length(elecave)-binwidth)){
#   temp <- elecave[t:(t+binwidth-1)]
#   spec <- fft(temp)/binwidth
#   fspec2[t] <- abs(spec[tindex])
# times <- -499:13500
# plot(times,fspec,type='l',col=colpal[1])
# lines(times,fspec2,col='green')

# all electrodes, condition 6 @ 7Hz
# all electrodes, condition 8 @ 5Hz
# target electrodes, conditions 1-14 for CRF, 5&7Hz
# target electrodes, full timecourse at 5 & 7Hz, conditions 6, 8, 13
# allwaves dimensions: 67 x 14 x 64 x 14000

# temp <- allwaves[,6,,2001:12000]
# meantemp <- apply(allwaves,2:3,mean)

# temp <- allwaves[,6,,2001:12000]
# meantemp <- apply(allwaves,2:3,mean)

f1 <- 7
f2 <- 5
    binwidth <- 1000
    tindex <- 1 + f1*(binwidth/1000)
    mindex <- 1 + f2*(binwidth/1000)
    tindex2 <- 1 + 2*f1*(binwidth/1000)
    mindex2 <- 1 + 2*f2*(binwidth/1000)

d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
EEGtimecourse5Hz <- array(0,dim=c(length(d),3,13000))
EEGtimecourse7Hz <- array(0,dim=c(length(d),3,13000))
EEGtimecourse10Hz <- array(0,dim=c(length(d),3,13000))
EEGtimecourse14Hz <- array(0,dim=c(length(d),3,13000))

for (s in 1:length(d)){
  load(d[s])
  targetchannels <- match(targetelectrodes, electrodes) - 2
  for (cond in 1:3){
    temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,],na.rm=TRUE)
    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
    temp[nainds] <- 0   # replace with zeros

fspec1 <- NULL
fspec2 <- NULL
fspec3 <- NULL
fspec4 <- NULL
for (t in 1:(14000-binwidth)){
  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
  fspec1[t] <- spec[tindex]
  fspec2[t] <- spec[mindex]
  fspec3[t] <- spec[tindex2]
  fspec4[t] <- spec[mindex2]

}
    EEGtimecourse5Hz[s,cond,] <- fspec1
    EEGtimecourse7Hz[s,cond,] <- fspec2
    EEGtimecourse10Hz[s,cond,] <- fspec3
    EEGtimecourse14Hz[s,cond,] <- fspec4

@@

>>>>

---
title: 'The Dynamics of Normalization Reweighting (target journal: Neuron)'
author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd,
  Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade
date: "`r Sys.Date()`"
output:
  bookdown::pdf_document2:
    fig_caption: yes 
    toc: false   
    keep_tex: true
  word_document: default
  html_document: default
---

@@

processdata <- 0  # this flag determines the amount of processing, with 4 levels:
# 0 - do no processing, generate the pdf using existing versions of all scripts
# 1 - generate figures using the processed group data (requires XGB of storage)
# 2 - download processed individual data and analyse (requires XGB of storage)
# 3 - download all raw data and analyse (requires XGB of storage)

plotsmoothed <- 1 # either plot the raw data (0), or a smoothed spline (1)

@@

    binwidth <- 1000
    findex <- 1 + targetF*(binwidth/1000)
    findex[2] <- 1 + maskF*(binwidth/1000)
    findex[3] <- 1 + 2*targetF*(binwidth/1000)
    findex[4] <- 1 + 2*maskF*(binwidth/1000)

if (processdata>2){

@@

    condcounter <- (1:20) * 0
    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
    if (s < 10){d <- dir(path = paste0(tempdir,'S0',s), pattern='*.csv.gz',full.names=TRUE)}
    if (s > 9){d <- dir(path = paste0(tempdir,'S',s), pattern='*.csv.gz',full.names=TRUE)}

@@

    for (block in 1:length(d)) {
      EEGdata <- read.csv(d[block], header = TRUE)

@@

      # epoch the data, Fourier transform and store
      triggertimes <- (1:40) * 0
      counter <- 0
      for (n in 1500:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
        if (EEGdata$Trigger[n] %in% legaltriggers) {
          counter <- counter + 1
          triggertimes[counter] <- n
      }
      }

      for (tr in 1:counter) {
        cond <- EEGdata$Trigger[triggertimes[tr]] / 10
        condcounter[cond] <- condcounter[cond] + 1
        for (ch in 1:64){
        temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-1499, ch + 2])
        temp <- temp - mean(temp[501:1500])
        allsamples[condcounter[cond],cond,ch,1:(1000*duration)] <- as.vector(rowMeans(temp))
        }
      }
    }
allsamples[which(is.na(allsamples))] <- 0     # remove any NaN values
meanwaveforms <- array(0,dim=c(14,64,14000))
trialsincluded <- matrix(0,nrow=14,ncol=64)
    for (cond in 1:14){
      for (ch in 1:64){
        temp <- allsamples[1:condcounter[cond],cond,ch,]
        allspec <- matrix(0,nrow=condcounter[cond],ncol=10000)
        for (trial in 1:condcounter[cond]){
          allspec[trial,] <- fft(temp[trial,2501:12500])/10000
        }
        targetresps <- allspec[,tindex]
        maskresps <- allspec[,mindex]
      if (sum(abs(targetresps))>0){  
      tempxy <- data.frame(Re(targetresps),Im(targetresps))
      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      i1 <- (D<3)
      tempxy <- data.frame(Re(maskresps),Im(maskresps))
      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
      i2 <- (D<3)
      i <- which((i1*i2)>0)
        meanwaveforms[cond,ch,] <- colMeans(temp[i,])
        trialsincluded[cond,ch] <- length(i)
      }
      }
    }

     save(file = paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'), list = c('meanwaveforms','electrodes','trialsincluded'))

    for (block in 1:length(d)){file.remove(d[block])}

  }
}
}
}

if (processdata>1){

d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
EEGtimecourse <- array(0,dim=c(length(d),length(findex),3,13000))
EEGspectra <- array(0,dim=c(length(d),3,20*10))
EEGscalpresps <- array(0,dim=c(length(d),4,14,64))
EEGallconds <- array(0,dim=c(length(d),4,14))

for (s in 1:length(d)){
  load(d[s])
  targetchannels <- match(targetelectrodes, electrodes) - 2

  for (cond in 1:14){
    temp <- colMeans(meanwaveforms[cond,targetchannels,],na.rm=TRUE)
        nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
    temp[nainds] <- 0   # replace with zeros
    spec <- fft(temp[2501:12500])/10000
    EEGallconds[s,1,cond] <- spec[1+(10*targetF)]
    EEGallconds[s,2,cond] <- spec[1+(10*maskF)]
    EEGallconds[s,3,cond] <- spec[1+(2*10*targetF)]
    EEGallconds[s,4,cond] <- spec[1+(2*10*maskF)]
  }
  for (cond in 1:3){
    temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,],na.rm=TRUE)
    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
    temp[nainds] <- 0   # replace with zeros

    spec <- fft(temp[2501:12500])/10000
    EEGspectra[s,cond,] <- spec[1:(20*10)]

for (t in 1:(14000-binwidth)){
  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
  for (f in 1:length(findex)){
  EEGtimecourse[s,f,cond,t] <- spec[findex[f]]
  }
}
  }

for (cond in 1:14){
  for (ch in 1:64){
     temp <- meanwaveforms[cond,ch,]
    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
    temp[nainds] <- 0   # replace with zeros
   spec <- fft(temp[2501:12500])/10000
   EEGscalpresps[s,1,cond,ch] <- spec[(targetF*10)+1]
   EEGscalpresps[s,2,cond,ch] <- spec[(maskF*10)+1]
   EEGscalpresps[s,3,cond,ch] <- spec[(2*targetF*10)+1]
   EEGscalpresps[s,4,cond,ch] <- spec[(2*maskF*10)+1]
  }
}

@@

save(file='temp/Pilotsummary.RData',list=c('EEGtimecourse','electrodes','EEGscalpresps','EEGspectra','EEGallconds'))
}

if (processdata>0){

load('temp/Pilotsummary.RData')
nsubjs <- dim(EEGtimecourse)[1]
EEGmeantimes <- array(0,dim=c(length(findex),3,13000))
EEGSEtimes <- array(0,dim=c(length(findex)+1,3,13000))
EEGmaskindices <- array(0,dim=c(length(findex)+1,13000))
EEGmaskSE <- array(0,dim=c(length(findex)+1,13000))
EEGmeanscalp <- abs(apply(abs(EEGscalpresps),2:4,mean))
EEGmeanspec <- abs(apply(abs(EEGspectra),2:3,mean))
EEGmeanconds <- apply(abs(EEGallconds),2:3,mean)
EEGcondsSE <- apply(abs(EEGallconds),2:3,sd)/sqrt(nsubjs)

for (f in 1:length(findex)){
for (cond in 1:3){
EEGmeantimes[f,cond,] <- apply(abs(EEGtimecourse[,f,cond,]),2,mean,na.rm=TRUE)
EEGSEtimes[f,cond,] <- apply(abs(EEGtimecourse[,f,cond,]),2,sd,na.rm=TRUE)/sqrt(nsubjs)
}}

EEGmaskindices[1,] <- colMeans(20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])))
EEGmaskindices[2,] <- colMeans(20*log10(abs(EEGtimecourse[,2,2,])/abs(EEGtimecourse[,2,3,])))
EEGmaskindices[3,] <- colMeans(20*log10(abs(EEGtimecourse[,3,1,])/abs(EEGtimecourse[,3,3,])))
EEGmaskindices[4,] <- colMeans(20*log10(abs(EEGtimecourse[,4,2,])/abs(EEGtimecourse[,4,3,])))

meanindices <- (20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])) + 20*log10(abs(EEGtimecourse[,2,2,])/abs(EEGtimecourse[,2,3,])) + 20*log10(abs(EEGtimecourse[,3,1,])/abs(EEGtimecourse[,3,3,])) + 20*log10(abs(EEGtimecourse[,4,2,])/abs(EEGtimecourse[,4,3,])))/4
EEGmaskindices[5,] <- colMeans(meanindices)

EEGmaskSE[1,] <- apply(20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])),2,sd)/sqrt(nsubjs)
EEGmaskSE[2,] <- apply(20*log10(abs(EEGtimecourse[,2,2,])/abs(EEGtimecourse[,2,3,])),2,sd)/sqrt(nsubjs)
EEGmaskSE[3,] <- apply(20*log10(abs(EEGtimecourse[,3,1,])/abs(EEGtimecourse[,3,3,])),2,sd)/sqrt(nsubjs)
EEGmaskSE[4,] <- apply(20*log10(abs(EEGtimecourse[,4,2,])/abs(EEGtimecourse[,4,3,])),2,sd)/sqrt(nsubjs)
EEGmaskSE[5,] <- apply(meanindices,2,sd)/sqrt(nsubjs)

times <- (-999:12000)/1000

plotlims <- c(-1,12,0,1)
ticklocsx <- c(-1,seq(0,12,2))    # locations of tick marks on y axis
ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))

if (plotsmoothed==0){
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[1,1,]+EEGSEtimes[1,1,],EEGmeantimes[1,1,13000:1]-EEGSEtimes[1,1,13000:1]),col=colpal[1],border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[1,2,]+EEGSEtimes[1,2,],EEGmeantimes[1,2,13000:1]-EEGSEtimes[1,2,13000:1]),col='grey',border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[1,3,]+EEGSEtimes[1,3,],EEGmeantimes[1,3,13000:1]-EEGSEtimes[1,3,13000:1]),col=colpal[2],border=NA)

lines(times,EEGmeantimes[1,1,],col=colpal[1])
lines(times,EEGmeantimes[1,2,],col='grey')
lines(times,EEGmeantimes[1,3,],col=colpal[2])
}
if (plotsmoothed==1){

spl5aU <- smooth.spline(times,EEGmeantimes[1,1,]+EEGSEtimes[1,1,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[1,1,]-EEGSEtimes[1,1,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[1,2,]+EEGSEtimes[1,2,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[1,2,]-EEGSEtimes[1,2,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[1,3,]+EEGSEtimes[1,3,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[1,3,]-EEGSEtimes[1,3,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)

spl5a <- smooth.spline(times,EEGmeantimes[1,1,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[1,2,],df=20)
lines(spl5a$x,spl5a$y,col='grey',lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[1,3,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
}
text(10,0.95,'7Hz',cex=2)

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))

if (plotsmoothed==0){
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[2,2,]+EEGSEtimes[2,2,],EEGmeantimes[2,2,13000:1]-EEGSEtimes[2,2,13000:1]),col=colpal[1],border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[2,1,]+EEGSEtimes[2,1,],EEGmeantimes[2,1,13000:1]-EEGSEtimes[2,1,13000:1]),col='grey',border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[2,3,]+EEGSEtimes[2,3,],EEGmeantimes[2,3,13000:1]-EEGSEtimes[2,3,13000:1]),col=colpal[2],border=NA)

lines(times,EEGmeantimes[2,2,],col=colpal[1])
lines(times,EEGmeantimes[2,1,],col='grey')
lines(times,EEGmeantimes[2,3,],col=colpal[2])
}
if (plotsmoothed==1){

spl5aU <- smooth.spline(times,EEGmeantimes[2,2,]+EEGSEtimes[2,2,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[2,2,]-EEGSEtimes[2,2,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[2,1,]+EEGSEtimes[2,1,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[2,1,]-EEGSEtimes[2,1,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[2,3,]+EEGSEtimes[2,3,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[2,3,]-EEGSEtimes[2,3,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)

spl5a <- smooth.spline(times,EEGmeantimes[2,2,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[2,1,],df=20)
lines(spl5a$x,spl5a$y,col='grey',lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[2,3,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
}
text(10,0.95,'5Hz',cex=2)

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))

if (plotsmoothed==0){
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[3,1,]+EEGSEtimes[3,1,],EEGmeantimes[3,1,13000:1]-EEGSEtimes[3,1,13000:1]),col=colpal[1],border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[3,2,]+EEGSEtimes[3,2,],EEGmeantimes[3,2,13000:1]-EEGSEtimes[3,2,13000:1]),col='grey',border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[3,3,]+EEGSEtimes[3,3,],EEGmeantimes[3,3,13000:1]-EEGSEtimes[3,3,13000:1]),col=colpal[2],border=NA)

lines(times,EEGmeantimes[3,1,],col=colpal[1])
lines(times,EEGmeantimes[3,2,],col='grey')
lines(times,EEGmeantimes[3,3,],col=colpal[2])
}
if (plotsmoothed==1){

spl5aU <- smooth.spline(times,EEGmeantimes[3,1,]+EEGSEtimes[3,1,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[3,1,]-EEGSEtimes[3,1,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[3,2,]+EEGSEtimes[3,2,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[3,2,]-EEGSEtimes[3,2,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[3,3,]+EEGSEtimes[3,3,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[3,3,]-EEGSEtimes[3,3,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)

spl5a <- smooth.spline(times,EEGmeantimes[3,1,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[3,2,],df=20)
lines(spl5a$x,spl5a$y,col='grey',lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[3,3,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
}
text(10,0.95,'14Hz',cex=2)

plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))

if (plotsmoothed==0){
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[4,2,]+EEGSEtimes[4,2,],EEGmeantimes[4,2,13000:1]-EEGSEtimes[4,2,13000:1]),col=colpal[1],border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[4,1,]+EEGSEtimes[4,1,],EEGmeantimes[4,1,13000:1]-EEGSEtimes[4,1,13000:1]),col='grey',border=NA)
polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[4,3,]+EEGSEtimes[4,3,],EEGmeantimes[4,3,13000:1]-EEGSEtimes[4,3,13000:1]),col=colpal[2],border=NA)

lines(times,EEGmeantimes[4,2,],col=colpal[1])
lines(times,EEGmeantimes[4,1,],col='grey')
lines(times,EEGmeantimes[4,3,],col=colpal[2])
}
if (plotsmoothed==1){

spl5aU <- smooth.spline(times,EEGmeantimes[4,2,]+EEGSEtimes[4,2,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[4,2,]-EEGSEtimes[4,2,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[4,1,]+EEGSEtimes[4,1,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[4,1,]-EEGSEtimes[4,1,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)

spl5aU <- smooth.spline(times,EEGmeantimes[4,3,]+EEGSEtimes[4,3,],df=20)
spl5aL <- smooth.spline(times,EEGmeantimes[4,3,]-EEGSEtimes[4,3,],df=20)
polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)

spl5a <- smooth.spline(times,EEGmeantimes[4,2,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[4,1,],df=20)
lines(spl5a$x,spl5a$y,col='grey',lwd=2)
spl5a <- smooth.spline(times,EEGmeantimes[4,3,],df=20)
lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
}
text(10,0.95,'10Hz',cex=2)

postscript("suppression.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)

plotlims <- c(-1,12,-3,6)
ticklocsx <- c(-1,seq(0,12,2))    # locations of tick marks on y axis
ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)

polygon(c(0,11,11,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))

lines(c(-1,12),c(0,0),lty=2)

if (plotsmoothed==0){
